Efficient pedigree recording for fast population genetics simulation

### 2017-11-18 forwards_paper.tex
Comments on tables section

Given a set of node and edge tables as described above,
there are a small set of requirements that ensure the tables
describe a valid tree sequence.
(There are essentially no such requirements on the site and mutation tables.)
These are:
\begin{enumerate}
    \item Offspring must be born after their parents (and hence, no loops).
    \item The set of intervals on which each individual is a child must be disjoint.
\end{enumerate}
A pair of node and edge tables that satisfy these two requirements
is guarenteed to uniquely describe at each point on the genome
a collection of directed, acyclic graphs -- in other words, a forest of trees.
For some applications it is necessary to check that at every point
there is only a \emph{single} tree.  
Checking this is more difficult, but is implemented in \msprime{}'s API.

For efficiency, \msprime{} makes several other sortedness requirements on the tables,
that are not necessarily satisfied by tabled emitted by a forwards-time simulation.
These can be rectified by first sorting (using \texttt{sort\_tables})
and then using \texttt{simplify}, which works on sorted tables
and is guarenteed to produce a valid, \msprime{}-ready tree sequence.

Note that since each node time is equal to the amount of time since the \emph{birth} of the
corresponding parent, time is measured in clock time, not in meioses.

>>>>

Given a set of node and edge tables as described above,
there are a small set of requirements that ensure the tables
describe a valid tree sequence.
(There are essentially no such requirements on the site and mutation tables.)
These are:
\begin{enumerate}
    \item Offspring must be born after their parents (and hence, no loops).
    \item The set of intervals on which each individual is a child must be disjoint.
\end{enumerate}
A pair of node and edge tables that satisfy these two requirements
is guarenteed to uniquely describe at each point on the genome
a collection of directed, acyclic graphs -- in other words, a forest of trees.
For some applications it is necessary to check that at every point
there is only a \emph{single} tree.  
Checking this is more difficult, but is implemented in \msprime{}'s API.
\jda{TODO add function name}

For efficiency, \msprime{} makes several other sortedness requirements on the tables,
that are not necessarily satisfied by tables emitted by a forwards-time simulation.
Fortunately, \msprime{}'s API includes tools to rectify this by first sorting (using \texttt{sort\_tables})
and then using \texttt{simplify}, which works on sorted tables
and is guarenteed to produce a valid, \msprime{}-ready tree sequence.

Note that since each node time is equal to the amount of time since the \emph{birth} of the
corresponding parent, time is measured in clock time, not in meioses.
\jda{is this the right place? I'd put it in discussion of Figure~\ref{fig:example_tree_sequence}}
